Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2012-04-03 article.tex
Increased DCC version number
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1486 ccdd05d5-56c1-461a-bf98-85f6876523b4
M -> Mt
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1488 ccdd05d5-56c1-461a-bf98-85f6876523b4

In the quadrupole approximation, the instantaneous frequency of the GW inspiral signal is related to the time $t$ relative to coalescence ~\citep{kidder1992, findchirppaper} through
%
\begin{equation} \label{eq:fgw}
	f(t) = \frac{1}{\pi \mathcal{M}}
		\left[ \frac{5}{256}\frac{\mathcal{M}}{t} \right]^{3/8}
\end{equation}
%
where $\mathcal{M} = M^{2/5} \mu^{3/5}$ is the chirp mass of the binary in units of time ($G
M_\odot / c^3 \approx 5$~$\upmu$s), $M$ is the total mass, and $\mu$ is the reduced mass. 
The expected value of the single detector \SNR\ for an optimally oriented (source at detector's zenith or nadir, orbital plane face-on) inspiral source is~\citep{Abadie:2010p10836}
%
\begin{equation}
	\label{eq:expected-snr}
	\rho =
		\frac{\mathcal{M}^{5/6} c}{\pi^{2/3} D}
		\sqrt{
			\frac{5}{6} \int_{f_\mathrm{low}}^{f_\mathrm{high}}
			\frac{f^{-7/3}}{S(f)} \mathrm{d}f}
\end{equation}
%
where $D$ is the luminosity distance and $S(f)$ is the one-sided power spectral density of the detector noise.  $f_\mathrm{low}$ and $f_\mathrm{high}$ are low and high frequency limits of integration which may be chosen to extend across the entire bandwidth of the detector.  If we want to trigger at a time $t$ before merger, then we must cut off the SNR integration at $f_\mathrm{high} = f(t)$ with $f(t)$ given by equation~(\ref{eq:fgw}) above.

@@

This paper has \LIGO\ Document Number {LIGO-P0900004-v32}.

>>>>

In the quadrupole approximation, the instantaneous frequency of the GW inspiral signal is related to the time $t$ relative to coalescence ~\citep{kidder1992, findchirppaper} through
%
\begin{equation} \label{eq:fgw}
	f(t) = \frac{1}{\pi \mathcal{M}_\mathrm{t}}
		\left[ \frac{5}{256}\frac{\mathcal{M}_\mathrm{t}}{t} \right]^{3/8}
\end{equation}
%
where $\mathcal{M}=M^{2/5} \mu^{3/5}$ is the chirp mass of the binary, $\mathcal{M}_\mathrm{t}=G \mathcal{M} / c^3$ is the chirp mass in units of time, $M$ is the total mass, and $\mu$ is the reduced mass. 
The expected value of the single detector \SNR\ for an optimally oriented (source at detector's zenith or nadir, orbital plane face-on) inspiral source is~\citep{Abadie:2010p10836}
%
\begin{equation}
	\label{eq:expected-snr}
	\rho =
		\frac{{\mathcal{M}_\mathrm{t}}^{5/6} c}{\pi^{2/3} D}
		\sqrt{
			\frac{5}{6} \int_{f_\mathrm{low}}^{f_\mathrm{high}}
			\frac{f^{-7/3}}{S(f)} \mathrm{d}f}
\end{equation}
%
where $D$ is the luminosity distance and $S(f)$ is the one-sided power spectral density of the detector noise.  $f_\mathrm{low}$ and $f_\mathrm{high}$ are low and high frequency limits of integration which may be chosen to extend across the entire bandwidth of the detector.  If we want to trigger at a time $t$ before merger, then we must cut off the SNR integration at $f_\mathrm{high} = f(t)$ with $f(t)$ given by equation~(\ref{eq:fgw}) above.

@@

This paper has \LIGO\ Document Number {LIGO-P0900004-v33}.
